A hierarchical model to evaluate pest treatments from prevalence and intensity data

### 2023-09-20 Article.qmd
Corrections asked by Reviewer 1 and Reviewer 2

The model and codes presented in this paper can be easily implemented to analyze a diversity of pest trials and surveys including prevalence and/or intensity data.

>>>>

Although our framework was illustrated to compare the efficacy of plant pest treatments, it could be applied to other areas of research in the future, in particular for optimizing designs used in animal and human epidemiology. It is imperative to note that the ultimate selection of a design should be contingent upon the consideration of localized constraints. As the model codes are made fully available, we believe that these codes could be used by different institutes to compare many different designs in the future, not only the types of designs considered in our paper. Of particular significance is the capability of our model to optimize sample sizes, with its impact contingent on the relative importance of within-trial variability compared to between-trial variability.
